---
title: "Using the Convertmetrics Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the convertmetrics package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Convert Metrics

The package convertmetrics is designed to convert some metrics from different measurement systems within R. It includes weight, volume, temperature, and distance. The hope is that work, school, personal projects, and more are made easier when working with different measurement systems. 

Let's see how we can accomplish this. First, load the `convertmetrics` package.
```{r setup}
library(convertmetrics)
```

Then, use the `distance()`, `weight()`, `volume()`, or `temp()` functions to convert a number with a specific unit to the other. We will take a look at the conversion between `g` and `tael` in weight. Assuming that we want to convert `8 gal` to `l`, so we will set the `num` argument equal to 8, `starting_unit` equals to `gal`, and `final_unit` equals to `l`.

```{r}
volume(num = 8, starting_unit = "gal", final_unit = "l")
```
Suppose that we also want to convert `c(3, NA, 5) g` to `taels`, so we will set the `num` argument equal to `c(3, NA, 5)`, `starting_unit` equals to `g`, and `final_unit` equals to `tael`. The function will discard the NA values.
```{r}
weight(num = c(3, NA, 5), starting_unit = "g", final_unit = "tael")
```

## Conversion Data

The `convertmetrics` package also comes with a built-in data set describing 60 conversions. Some of the data points are repetitive, with the purpose of showing that this package can work with a large data frame.
```{r}
head(convertmetrics::convert_data)
```
Suppose that we also want to convert the first column (in `km`) to `mi`, so we will set the `num` argument equal to the first column of the convert_data dataset, `starting_unit` equals to `km`, and `final_unit` equals to `mi`.
```{r}
distance(num = convert_data$distance_km, starting_unit = "km", final_unit = "mi")
```
As we can see, the result equals to the second column of the dataset, which represents distance in miles.
